The regularity of ODEs and thimble integrals \\ with respect to Borel summation

### 2024-03-28 exp-resurgence.tex
Remove extra indices from Airy-Lucas argument
Also, mark revisions needed to bring this section up to date.

By the properties of the Laplace transform (we refer to Proposition~\ref{prop:L-int-op}), $\laplace_{\zeta, \alpha} v$ satisfies the differential equation~\eqref{eqn:reg-mod-bessel-AL} if and only if $v$ satisfies the integral equation
\begin{equation}\label{int-eq:spatial-mod-bessel-AL}
\left[ \big[ \zeta^2 - 1 \big] - \fracderiv{-1}{\zeta}{\alpha} \circ \zeta - \big(\tfrac{m}{n}\big)^2 \fracderiv{-2}{\zeta}{\alpha} \right] v = 0.
\end{equation}
It's tempting to differentiate both sides of this equation until we get
\begin{equation}\label{diff-eq:spatial-mod-bessel-AL}
\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ \big[ \zeta^2 - 1 \big] - \tfrac{\partial}{\partial \zeta} \circ \zeta - \big(\tfrac{m}{n}\big)^2 \right] v = 0,
\end{equation}
which is easier to solve. Unfortunately, a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} will not satisfy equation~\eqref{int-eq:spatial-mod-bessel-AL} in general. However, as we show in Section~\ref{shifting}, a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} {\em will} satisfy equation~\eqref{int-eq:spatial-mod-bessel-AL} if it belongs to $\singexpalg{\sigma}(\Omega_j)$, for some $\sigma\in (0,1)$.

This is great news, because equation~\eqref{diff-eq:spatial-mod-bessel-AL} has a regular singularity at each root of $\zeta^2 - 1$, and the Frobenius method often gives a solution of order $\sigma=1/2$ at each regular singular point. We can see the regular singularities by moving the derivatives to the right:
\[ \left[ (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{m}{n}\big)^2 \big] \right] v = 0. \]

In Sections \ref{pos-root-AL}\,--\,\ref{neg-root-AL}, we will see this approach succeed. For each root \textcolor{orange}{[switch to $\alpha$]} $\alpha_j$, we will find a solution $v_j$ of equation~\eqref{diff-eq:spatial-mod-bessel-AL} which is $\singexpalg{\sigma}(\Omega_j)$, for some $\sigma$, and $\Omega_j$ as in the figure from Theorem~\ref{re:thm:exist_uniq_ODE}. We know the function $\laplace_{\zeta, \alpha} v_\alpha$ will satisfy equation~\eqref{eqn:reg-mod-bessel-AL}, and we can even find its asymptotics from the order $\tau_\alpha$ of $v_\alpha$. We learned in Section~\ref{sec:change-translation} that
\[ \laplace_{\zeta, \alpha_j} v_j = e^{-\alpha_j z} V_j \]
where $V_j = \laplace_{\zeta_j, 0} v_\alpha$ and $\zeta = \alpha_j + \zeta_j$. We can see from Section~\ref{sec:reg-decay} that $V_j$ is asymptotic to a scalar multiple of $z^{-1 - \tau_j}$ at $z = \infty$, so the further decomposition
\[ \laplace_{\zeta, \alpha_j} v_j = e^{-\alpha_j z} z^{-\tau_j} W_j, \]
makes $W_j$ is asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.

@@

From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, 1} v_1$ satisfies equation~\eqref{eqn:mod-bessel-AL}, and can be written as $e^{-z} V_1$, where $V_1 = \laplace_{\zeta_1, 0} v_1$. Since $v_1$ has order $-1/2$, the decomposition $V_1 = z^{-1/2} W_1$ makes $W_1$ asymptotic to a scalar multiple of $1+O(z^{-1})$ at $z = \infty$.

@@

Let us find a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} which belongs to $\singexpalg{\sigma}(\Omega_{-1})$. In the rescaled coordinate from Section~\ref{pos-root-AL}, this is the point $\xi_1 = 1$. Looking again through Kummer's table of solutions, we find another expression \cite[formula~15.10.14]{dlmf} which belongs to $\singexpalg{1/2}$ at $\xi_1 = 1$:

@@

where $\zeta_{-1}$ is the coordinate with $\zeta = -1 + \zeta_{-1}$. From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, -1} v_{-1}$ satisfies equation~\eqref{eqn:mod-bessel-AL}, and can be written as $e^z V_{-1}$, where $V_{-1} = \laplace_{\zeta_{-1}, 0} v_{-1}$. Since $v_{-1}$, like our other solution, has order $-1/2$, the same decomposition $V_{-1} = z^{-1/2} W_{-1}$ makes $W_{-1}$ asymptotic to a scalar multiple of $1+O(z^{-1})$ at $z = \infty$.

In this example, $v_1$ and $v_{-1}$ happen to be related by a symmetry: the M\"{o}bius transformation that pulls $\zeta$ back to $-\zeta$. Kummer's solutions typically come from six different hypergeometric equations, which are related by the M\"{o}bius transformations that permute their singularities. In our case, though, exchanging $1$ with $-1$ keeps equation~\eqref{diff-eq:spatial-mod-bessel-AL} the same.
\subsubsection{Abstract argument for Borel regularity}\label{bessel-regularity-AL}
The analysis in Sections~\ref{big-idea}--\ref{neg-root-AL} picks out a frame in the space of analytic solutions of~\eqref{eqn:reg-mod-bessel-AL}. The frame is generated by solutions of the form $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$, with $v_j\in\singexpalg{1/2}(\Omega_j)$.
\begin{verify}
We get $v_j$ from the existence result in Section~\ref{borel_reg-ODE}, which gives $v_j = \zeta^{\tau-1} + v_j'$ with $\tau \in (0, \infty)$ and $v_j' \in \holoL{\infty, 1-\tau-\epsilon}(\Omega)$ \textcolor{magenta}{[What is this space? Doesn't match notation from {\tt reg-sing-volterra}]} for some $\epsilon \in (0, 1]$. Looking back at the definitions of our weighted $L^\infty$ spaces, we can see that
\begin{align*}
v_j' \in \holoL{\infty, 1-\tau-\epsilon}(\Omega) & \Longrightarrow \zeta_j^{1-\tau-\epsilon}\,v_j' \text{ is bounded near } \zeta_j = 0 \\
& \Longrightarrow \zeta_j^\epsilon\,\zeta_j^{1-\tau-\epsilon}\,v_j' \text{ goes to } 0 \text{ as } \zeta_j \text{ goes to } 0 \\
& \Longrightarrow \zeta_j^{1-\tau}\,v_j' \text{ goes to } 0 \text{ as } \zeta_j \text{ goes to } 0 \\
& \Longrightarrow v_j' / \zeta_j^{\tau-1} \text{ goes to } 0 \text{ as } \zeta_j \text{ goes to } 0 \\
& \Longleftrightarrow v_j' \in o\big(\zeta_j^{\tau-1}\big).
\end{align*}
In this case, $\tau = \tfrac{1}{2}$.
\end{verify}

@@

The Borel transform maps $e^{-\alpha_j z} z^{-1/2}\,\C\llbracket z^{-1} \rrbracket$ into $\zeta_j^{-1/2}\,\C\llbracket \zeta_j \rrbracket$ (see Section \ref{sec:action_transseries}), and it turns formal trans-monomial solutions of equation~\eqref{eqn:reg-mod-bessel-AL} into formal power series solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL}. Summation sends convergent power series in $\zeta_j^{-1/2}\,\C\llbracket \zeta_j \rrbracket$ into $\zeta_j^{-1/2}+ o\big(\zeta_j^{-1/2}\big)$ \textcolor{orange}{[since the argument above is one-way, isn't this weaker than being in $\singexpalg{1/2}$?]}, and it turns convergent power series that satisfy a given fractional integral equation into holomorphic functions that satisfy the same equation \cite[Lemma 2]{reg-sing-volterra}. Thus, if $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$ are $1$-Gevrey, their Borel transforms sum to solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL}, which lie in $\singexpalg{1/2}$ \textcolor{orange}{[needs domain]} for $\alpha = 1$ and $\alpha = -1$, respectively.

When $\alpha$ is $1$ or $-1$, equation~\eqref{int-eq:spatial-mod-bessel-AL} becomes the kind of singular integral equation discussed in Section~\ref{borel_reg-ODE}. It therefore has exactly one solution in $\singexpalg{1/2}$ \textcolor{orange}{[needs domain]}, up to scaling. That means $\borel\big[ e^{-\alpha_j z} z^{-1/2}\,\tilde{W}_j \big]$ must sum to a scalar multiple of $v_j$. Thus, if $e^{-\alpha_j z} z^{-1/2}\,\tilde{W}_j$ is Borel-summable, its Borel sum is a scalar multiple of $\laplace_{\zeta, \alpha_j} v_j$.

>>>>

By the properties of the Laplace transform (we refer to Proposition~\ref{prop:L-int-op}), $\laplace_{\zeta, \alpha} v$ satisfies the differential equation~\eqref{eqn:reg-mod-bessel-AL} if and only if $v$ satisfies the integral equation
\begin{equation}\label{int-eq:spatial-mod-bessel-AL}
\left[ \big[ \zeta^2 - 1 \big] - \fracderiv{-1}{\zeta}{\alpha} \circ \zeta - \big(\tfrac{m}{n}\big)^2 \fracderiv{-2}{\zeta}{\alpha} \right] v = 0.
\end{equation}
It's tempting to differentiate both sides of this equation until we get
\begin{equation}\label{diff-eq:spatial-mod-bessel-AL}
\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ \big[ \zeta^2 - 1 \big] - \tfrac{\partial}{\partial \zeta} \circ \zeta - \big(\tfrac{m}{n}\big)^2 \right] v = 0,
\end{equation}
which is easier to solve. Unfortunately, a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} will not satisfy equation~\eqref{int-eq:spatial-mod-bessel-AL} in general. However, as we show in Section~\ref{shifting}, a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} {\em will} satisfy equation~\eqref{int-eq:spatial-mod-bessel-AL} if it belongs to $\singexpalg{\sigma}(\Omega_j)$, for some $\sigma\in (-1, 0)$.

This is great news, because equation~\eqref{diff-eq:spatial-mod-bessel-AL} has a regular singularity at each root of $\zeta^2 - 1$, and the Frobenius method often gives a solution \textcolor{magenta}{of order $\sigma=1/2$} at each regular singular point. We can see the regular singularities by moving the derivatives to the right:
\[ \left[ (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{m}{n}\big)^2 \big] \right] v = 0. \]

In Sections \ref{pos-root-AL}\,--\,\ref{neg-root-AL}, we will see this approach succeed. For each root $\alpha$, we will find a solution $v_\alpha$ of equation~\eqref{diff-eq:spatial-mod-bessel-AL} which is in $\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$ for some constant $\tau_\alpha \in (0, 1)$ and some domain $\Omega_\alpha$ resembling the one in the figure from Theorem~\ref{re:thm:exist_uniq_ODE}. We know the function $\laplace_{\zeta, \alpha} v_\alpha$ will satisfy equation~\eqref{eqn:reg-mod-bessel-AL}, \textcolor{magenta}{and we can even find its asymptotics from the order $\tau_\alpha$ of $v_\alpha$}. We learned in Section~\ref{sec:change-translation} that
where $V_\alpha = \laplace_{\zeta_\alpha, 0} v_\alpha$ and $\zeta = \alpha + \zeta_\alpha$. We can see from Section~\ref{sec:reg-decay} that $V_\alpha$ is asymptotic to a scalar multiple of $z^{-1 - \tau_\alpha}$ at $z = \infty$, so the further decomposition
makes $W_\alpha$ asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.

@@

From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, 1} v_1$ satisfies equation~\eqref{eqn:mod-bessel-AL}, and can be written as $e^{-z} V_1$, where $V_1 = \laplace_{\zeta_1, 0} v_1$. Since $v_1$ \textcolor{magenta}{has order $-1/2$}, the decomposition $V_1 = z^{-1/2} W_1$ makes $W_1$ asymptotic to a scalar multiple of $1+O(z^{-1})$ at $z = \infty$.

@@

Let us find a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} which belongs to $\singexpalg{\sigma}(\Omega_{-1})$. In the rescaled coordinate from Section~\ref{pos-root-AL}, this is the point $\xi_1 = 1$. Looking again through Kummer's table of solutions, we find another expression \cite[formula~15.10.14]{dlmf} which \textcolor{magenta}{belongs to $\singexpalg{-1/2}$ at $\xi_1 = 1$}:

@@

where $\zeta_{-1}$ is the coordinate with $\zeta = -1 + \zeta_{-1}$. From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, -1} v_{-1}$ satisfies equation~\eqref{eqn:mod-bessel-AL}, and can be written as $e^z V_{-1}$, where $V_{-1} = \laplace_{\zeta_{-1}, 0} v_{-1}$. Since $v_{-1}$, like our other solution, \textcolor{magenta}{has order $-1/2$}, the same decomposition $V_{-1} = z^{-1/2} W_{-1}$ makes $W_{-1}$ asymptotic to a scalar multiple of $1+O(z^{-1})$ at $z = \infty$.

In this example, $v_1$ and $v_{-1}$ happen to be related by a symmetry: the M\"{o}bius transformation that pulls $\zeta$ back to $-\zeta$. Kummer's solutions typically come from six different hypergeometric equations, which are related by the M\"{o}bius transformations that permute their singularities. In our case, though, exchanging $1$ with $-1$ keeps equation~\eqref{diff-eq:spatial-mod-bessel-AL} the same.
\subsubsection{Abstract argument for Borel regularity}\label{bessel-regularity-AL}
The analysis in Sections~\ref{big-idea}--\ref{neg-root-AL} picks out a frame in the space of analytic solutions of~\eqref{eqn:reg-mod-bessel-AL}. The frame is generated by solutions of the form $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$, with $v_\alpha \in \singexpalg{-1/2}(\Omega_\alpha)$.
\begin{verify}
We get $v_\alpha$ from the existence result in Section~\ref{borel_reg-ODE}, which gives $v_\alpha = \zeta^{\tau_\alpha-1} + v_\alpha'$ with $\tau \in (0, \infty)$ and $v_j' \in \holoL{\infty, 1-\tau-\epsilon}(\Omega)$ \textcolor{magenta}{[What is this space? Doesn't match notation from {\tt reg-sing-volterra}]} for some $\epsilon \in (0, 1]$. Looking back at the definitions of our weighted $L^\infty$ spaces, we can see that
\begin{align*}
v_j' \in \holoL{\infty, 1-\tau-\epsilon}(\Omega) & \Longrightarrow \zeta_j^{1-\tau-\epsilon}\,v_j' \text{ is bounded near } \zeta_j = 0 \\
& \Longrightarrow \zeta_j^\epsilon\,\zeta_\alpha^{1-\tau-\epsilon}\,v_j' \text{ goes to } 0 \text{ as } \zeta_\alpha \text{ goes to } 0 \\
& \Longrightarrow \zeta_\alpha^{1-\tau}\,v_\alpha' \text{ goes to } 0 \text{ as } \zeta_\alpha \text{ goes to } 0 \\
& \Longrightarrow v_\alpha' / \zeta_\alpha^{\tau_\alpha-1} \text{ goes to } 0 \text{ as } \zeta_\alpha \text{ goes to } 0 \\
& \Longleftrightarrow v_j' \in o\big(\zeta_\alpha^{\tau_\alpha-1}\big).
\end{align*}
In this case, $\tau_\alpha = \tfrac{1}{2}$.
\end{verify}

@@

The Borel transform maps $e^{-\alpha z} z^{-1/2}\,\C\llbracket z^{-1} \rrbracket$ into $\zeta_\alpha^{-1/2}\,\C\llbracket \zeta_j \rrbracket$ \textcolor{magenta}{(see Section \ref{sec:action_transseries})}, and it turns formal trans-monomial solutions of equation~\eqref{eqn:reg-mod-bessel-AL} into formal power series solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL}. Summation sends convergent power series in $\zeta_\alpha^{-1/2}\,\C\llbracket \zeta_\alpha \rrbracket$ into $\zeta_\alpha^{-1/2}+ o\big(\zeta_\alpha^{-1/2}\big)$ \textcolor{orange}{[since the argument above is one-way, isn't this weaker than being in $\singexpalg{-1/2}$?]}, and it turns convergent power series that satisfy a given fractional integral equation into holomorphic functions that satisfy the same equation \cite[Lemma 2]{reg-sing-volterra}. Thus, if $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$ are $1$-Gevrey, their Borel transforms sum to solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL}, which lie in $\singexpalg{-1/2}$ \textcolor{magenta}{[needs domain]} for $\alpha = 1$ and $\alpha = -1$, respectively.

When $\alpha$ is $1$ or $-1$, equation~\eqref{int-eq:spatial-mod-bessel-AL} becomes the kind of singular integral equation discussed in Section~\ref{borel_reg-ODE}. It therefore has exactly one solution in $\singexpalg{1/2}$ \textcolor{orange}{[needs domain]}, up to scaling. That means $\borel\big[ e^{-\alpha z} z^{-1/2}\,\tilde{W}_\alpha \big]$ must sum to a scalar multiple of $v_\alpha$. Thus, if $e^{-\alpha z} z^{-1/2}\,\tilde{W}_\alpha$ is Borel-summable, its Borel sum is a scalar multiple of $\laplace_{\zeta, \alpha} v_\alpha$.
